Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-04 doc/JFLA2022/paper.tex
Resurrect the definition of "LOC"

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq and in Lean's Mathlib amount to hundreds of thousands of lines and tens of thousands of definitions and theorems~\cite{Nie2020a, Mathlib}. However, after a key mathematical definition or result is added to a library, it must be \emph{documented and maintained}~\cite{vanDoorn2020,alectryonpaper}.

>>>>

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq and in Lean's Mathlib amount to hundreds of thousands of lines of code (LOC) and tens of thousands of definitions and theorems~\cite{Nie2020a, Mathlib}. However, after a key mathematical definition or result is added to a library, it must be \emph{documented and maintained}~\cite{vanDoorn2020,alectryonpaper}.
